Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD

### 2019-10-03 paper/cvpr2020/sections/introduction.tex
Teaser figure.

Our method is not without limitations. It still requires a laser and
single-pixel LiDAR detector, and as such, is sensitive to ambient photons. Being 
a variant of histogram matching, our method is unable to transpose the
values of pixels (i.e. if pixel $a$ is farther
than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
In other words, our method is not able to resolve ordinal depth errors
(errors where an object is wrongly placed closer or farther
relative to another object). Finally, our method is non-differentiable, and is
therefore unsuitable for end-to-end optimization of multi-part networks.

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{sections/figures/captured/midas/8_30_small_lab_scene/teaser.eps}
  \caption{Our method uses the SPAD's histogram to rescale the initial depth
    estimate from the CNN to align with the ground truth depth.}
  \label{fig:teaser}
\end{figure}
Our method is not without limitations. It still requires a laser and
single-pixel LiDAR detector, and as such, is sensitive to ambient photons. Being 
a variant of histogram matching, our method is unable to transpose the
values of pixels (i.e. if pixel $a$ is farther
than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
In other words, our method is not able to resolve ordinal depth errors
(errors where an object is wrongly placed closer or farther
relative to another object). Finally, our method is non-differentiable, and is
therefore unsuitable for end-to-end optimization of multi-part networks.
